Stateless Model Checking with Data-Race Preemption Points

### 2016-08-13 oopsla-16/evaluation.tex
Rerun nondet expt and update results in table/graph

\begin{table*}[t]
	\begin{center}
		\small
		\revisionx{
	\begin{tabular}{r|c||c|c|c|c|c||c|c||c|c}
		& {\bf Num.} & {\bf QS-LHB} & {\bf QS-PHB} & {\bf ICB} & {\bf DPOR} & {\bf ShMem} & {\bf LHB DR} & {\bf Nondet.} & {\bf Mutual} & {\bf Avg. tested} \\
		{\bf Test} & {\bf tested} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf DR bugs} & {\bf timeouts} & {\bf subset SSes} \\
		\hline
				% XXX FIXME: Need rerun nondet dr expt!
				% #test  qs-lhb  qs-phb   icb     dpor    everyw  dronly  nondets timeout comp.SSes
		{\tt bcast}	& 79	& 8	& 8	& 5	& 6	& 7	& 2	& 4	& 7	& 112.3	\\
		{\tt join} 	& 79	& 23	& 20	& 13	& 13 	& 14	& 11	& 6	& 11	& 75.9	\\
		{\tt mx} 	& 79	& 10	& 9	& 1	& 1	& 12	& 9	& 1	& 0	& -	\\
		{\tt sem} 	& 79	& 17	& 16	& 12	& 11	& 12	& 7	& 5	& 36	& 93.4	\\
		{\tt signal} 	& 79	& 10	& 8	& 5	& 5	& 11	& 6	& 6	& 45	& 59.0	\\
		{\tt rwlock} 	& 79	& 27	& 26	& 25	& 23	& 28	& 4	& 2	& 43	& 88.3	\\
		\hline
		{\tt sched} 	& 59	& 7	& 7	& 1	& 1	& 8	& 6	& 4	& 2	& 13.0	\\
		{\tt alarm} 	& 44	& 21	& 12	& 16	& 5	& 29	& 17	& 3	& 16	& 8.1	\\
		{\tt wait} 	& 52	& 30	& 27	& \revisionz{24}
								& 23	& 1	& 7	& 1	& 13	& 32.8	\\
		\hline
		{\bf Total}	& 629	& 153	& 133	& \revisionz{102}
								& 88	& 122	& 69	& 32	& 173	& 69.5 	\\
	\end{tabular}
		}
	\end{center}
	\caption{Summary of bugs
	%and data races
	found by each test program.
		\revisionx{QS-LHB and QS-PHB are \quicksand; ICB/DPOR/ShMem are the controls (\sect{\ref{sec:eval-setup}}).}
		``LHB DR bugs'' counts among \revisionx{QS-Limited-HB's} bugs how many required data-race PPs to expose (\sect{\ref{sec:eval-sssmc}});
	among those, ``Nondeterministic DR bugs'' counts how many candidates required MC integration to identify (\sect{\ref{sec:eval-dr}}).
	``Mutual timeouts'' counts how often both \revisionx{QS-Limited-HB and SSS-MC-ICB} timed out with no bug found;
	among those, ``Average tested subset SSes'' counts how many partial verifications \quicksand~provided on average for each test (\sect{\ref{sec:eval-sssmc}}).
		}
	\label{tab:drbugs}
\end{table*}

@@

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{nondet-drs-1-v2.pdf}
	\caption{Some data-race candidates may not be identified during a single program execution.
		Using nondeterministic data races as PPs,
		\quicksand~found 189\% as many data-race bugs compared to using single-pass candidates alone.
	}
	\label{fig:dr-falsenegs}
\end{figure}
Figure~\ref{fig:dr-falsenegs} compares the types of data-race candidates necessary to expose each data-race bug in our test suite.
The first series represents the bugs found using PPs from single-pass data-race candidates,
% not entirely true, as portend could be given data-race traces from an MC,
%but they don't do it in their paper, so i feel comfortable making this claim
i.e., the state-of-the-art approach used by \cite{racefuzzer,portend}.
The second series shows all data-race bugs \quicksand~found,
which includes the former type as well as new bugs involving nondeterministic data-races.
\quicksand~found 68 data-race bugs in total, only 36 of which could be found with single-pass data-race candidates alone.
%In total, we found 189\% as many bugs by using nondeterministic data-race candidates as PPs.

>>>>

\newcommand\revz[1]{\revisionz{#1}}

\begin{table*}[t]
	\begin{center}
		\small
		\revisionx{
	\begin{tabular}{r|c||c|c|c|c|c||c|c|c|c||c|c}
		\multicolumn{2}{c||}{} & \multicolumn{5}{c||}{\bf \revz{Total bugs}} & \multicolumn{4}{c||}{\bf \revz{Data-race bugs}} \\
		% ---
		& {\bf Num.} & \multicolumn{2}{c|}{\bf \revz{\quicksand}} & \multicolumn{3}{c||}{\bf \revz{Control (SSS-MC)}}
		& \multicolumn{2}{c|}{\bf \revz{Limited HB}} & \multicolumn{2}{c||}{\bf \revz{Pure HB}} &
		%& {\bf LHB DR} & {\bf Nondet.} & & &
		{\bf Mutual} & {\bf Avg. tested} \\
		% ---
		{\bf Test} & {\bf tested} & {\bf LHB} & {\bf PHB} & {\bf ICB} & {\bf DPOR} & {\bf ShMem}
		& {\bf All} & {\bf Nondet.} & {\bf \revz{All}} & {\bf \revz{Nondet.}}
		& {\bf timeouts} & {\bf subset SSes} \\
		% ---
		\hline
				% #test  qs-lhb  qs-phb           icb             dpor    everyw  dronly  nondets(LHB)    dronly(PHB)    nondets(LHB) mutualtimeout    comp.SSes
		{\tt bcast}	& 79	& 8	& 8		& 5		& 6	& 7	& 2	& \revz{1}	& \revz{2}	& \revz{1}	& 7		& 112.3	\\
		{\tt join} 	& 79	& 23	& 20		& 13		& 13 	& 14	& 11	& \revz{4}	& \revz{7}	& \revz{3}	& \revz{12}	& \revz{69.7}	\\
		{\tt mx} 	& 79	& 10	& 9		& 1		& 1	& 12	& 9	& \revz{1}	& \revz{8}	& \revz{1}	& 0		& -	\\
		{\tt sem} 	& 79	& 17	& 16		& 12		& 11	& 12	& 7	& \revz{3}	& \revz{6}	& \revz{2}	& \revz{50}	& \revz{77.4}	\\
		{\tt signal} 	& 79	& 10	& 8		& 5		& 5	& 11	& 6	& \revz{1}	& \revz{3}	& \revz{2}	& 45		& \revz{59.6}	\\
		{\tt rwlock} 	& 79	& 27	& 26		& 25		& 23	& 28	& 4	& \revz{1}	& \revz{3}	& \revz{0}	& \revz{44}	& \revz{86.3}	\\
		\hline
		{\tt sched} 	& 59	& 7	& 7		& 1		& 1	& 8	& 6	& \revz{4}	& \revz{6}	& \revz{6}	& 2		& 13.0	\\
		{\tt alarm} 	& 44	& 21	& 12		& 16		& 5	& 29	& 17	& \revz{1}	& \revz{7}	& \revz{6}	& \revz{17}	& \revz{7.8}	\\
		{\tt wait} 	& 52	& 30	& \revz{26}	& \revz{24}	& 23	& 1	& 7	& \revz{2}	& \revz{2}	& \revz{0}	& \revz{15}	& \revz{33.8}	\\
		\hline
		{\bf Total}	& 629	& 153	& \revz{132}	& \revz{102}	& 88	& 122	& 69	& \revz{15}	& \revz{44}	& \revz{21}	& \revz{192}	& \revz{65.8} 	\\
	\end{tabular}
		}
	\end{center}
	\caption{Summary of bugs
	%and data races
	found by each test program.
		\revisionx{QS-LHB and QS-PHB are \quicksand; ICB/DPOR/ShMem are the controls (\sect{\ref{sec:eval-setup}}).}
		``\revisionz{Data-race} bugs'' counts among \revisionz{\quicksand's} bugs how many required data-race PPs to expose (\sect{\ref{sec:eval-sssmc}});
	among those, \revisionz{the ``Nondeterministic'' columns show} how many candidates required MC integration to identify (\sect{\ref{sec:eval-dr}}).
	``Mutual timeouts'' counts how often both \revisionx{QS-Limited-HB and SSS-MC-ICB} timed out with no bug found;
	among those, ``Average tested subset SSes'' counts how many partial verifications \quicksand~provided on average for each test (\sect{\ref{sec:eval-sssmc}}).
		}
	\label{tab:drbugs}
\end{table*}

@@

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{nondets.pdf}
	\caption{Some data-race candidates may not be identified during a single program execution.
		Using nondeterministic data races as PPs,
		% lhb: 127.77%
		% phb: 191.30%
		\quicksand~found \revisionz{128\% (Limited HB) to 191\% (Pure HB)} as many data-race bugs compared to using single-pass candidates alone.
	}
	\label{fig:dr-falsenegs}
\end{figure}
Figure~\ref{fig:dr-falsenegs} compares the types of data-race candidates necessary to expose each data-race bug in our test suite.
The first series represents the bugs found using PPs from single-pass data-race candidates,
% not entirely true, as portend could be given data-race traces from an MC,
%but they don't do it in their paper, so i feel comfortable making this claim
i.e., the state-of-the-art approach used by \cite{racefuzzer,portend}.
The second series shows all data-race bugs \quicksand~found,
which includes the former type as well as new bugs involving nondeterministic data-races.
\revisionz{QS-LHB found 69 data-race bugs in total, 54} of which could be found with single-pass data-race candidates alone.
\revisionz{QS-PHB is even more dependent on nondeterministic data-race PPs, requiring nondeterministic data-race PPs in 21 cases among its 44 total data-race bugs.}
%In total, we found 189\% as many bugs by using nondeterministic data-race candidates as PPs.
